19Q1

### 2019-04-30 19Q1.Rmd
re-organized plots dir

@@

crispr_ge_spearman_corr_plot <- ggplot(data = crispr_spear_ge, aes(x = Gene, y = corr)) +
  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
  scale_fill_gradientn(colours = c("white", "deepskyblue4"), breaks = c(0, 3, 6, 9, 12, 15), labels = c(0, 3, 6, 9, 12, 15), limits = c(0, 15)) +
  coord_cartesian(ylim = c(-0.325, 0.325)) +
  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05), labels = seq(-0.4, 0.4, by = 0.05)) +
  theme(legend.position = c(0.15, 0.95), legend.direction = "horizontal", legend.key.size = unit(0.05, "npc"), axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
  labs(title = "Gene Expression", fill = expression(-log[10](p)), x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
  geom_curve(aes(x = 2, y = -0.262, xend = 13.7, yend = -0.112), color = "lightgray", curvature = -0.45, arrow = arrow(length = unit(0.03, "npc")))

crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spear_cn, aes(x = Gene, y = corr)) +
  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
  scale_fill_gradientn(colours = c("white", "green4"), breaks = c(0, 3, 6, 9, 12, 15), labels = c(0, 3, 6, 9, 12, 15), limits = c(0, 15)) +
  coord_cartesian(ylim = c(-0.325, 0.325)) +
  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05), labels = seq(-0.4, 0.4, by = 0.05)) +
  theme(legend.position = c(0.15, 0.95), legend.direction = "horizontal", legend.key.size = unit(0.05, "npc"), axis.title.y = element_blank(), axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
  labs(title = "Copy Number", fill = expression(-log[10](p)), x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
  geom_curve(aes(x = 2, y = -0.255, xend = 13.7, yend = -0.112), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))

@@

# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
```

@@

Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
```{r, eval=FALSE, fig.height=6, fig.width=12}
# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "KS")

>>>>

```{r}
crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

@@

crispr_ge_spearman_corr_plot <- ggplot(data = crispr_spear_ge, aes(x = Gene, y = corr)) +
  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
  scale_fill_gradientn(colours = c("white", "deepskyblue4"),
                       breaks = c(0, 3, 6, 9, 12, 15),
                       labels = c(0, 3, 6, 9, 12, 15),
                       limits = c(0, 15)) +
  coord_cartesian(ylim = c(-0.325, 0.325)) +
  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05),
                     labels = seq(-0.4, 0.4, by = 0.05)) +
  theme(legend.position = c(0.15, 0.95),
        legend.direction = "horizontal",
        legend.key.size = unit(0.05, "npc"),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
  labs(title = "Gene Expression",
       fill = expression(-log[10](p)),
       x = "Gene",
       y = expression("Spearman Correlation Coefficient"~(r[s]))) +
  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset),
                    xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
  geom_curve(aes(x = 2, y = -0.262, xend = 13.7, yend = -0.112),
             color = "lightgray", curvature = -0.45,
             arrow = arrow(length = unit(0.03, "npc")))

crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spear_cn, aes(x = Gene, y = corr)) +
  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
  scale_fill_gradientn(colours = c("white", "green4"),
                       breaks = c(0, 3, 6, 9, 12, 15),
                       labels = c(0, 3, 6, 9, 12, 15),
                       limits = c(0, 15)) +
  coord_cartesian(ylim = c(-0.325, 0.325)) +
  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05),
                     labels = seq(-0.4, 0.4, by = 0.05)) +
  theme(legend.position = c(0.15, 0.95),
        legend.direction = "horizontal",
        legend.key.size = unit(0.05, "npc"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
  labs(title = "Copy Number",
       fill = expression(-log[10](p)),
       x = "Gene",
       y = expression("Spearman Correlation Coefficient"~(r[s]))) +
  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset),
                    xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
  geom_curve(aes(x = 2, y = -0.255, xend = 13.7, yend = -0.112),
             color = "lightgray", curvature = -0.2,
             arrow = arrow(length = unit(0.03, "npc")))

@@

ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
```

@@

Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
```{r, eval=TRUE, fig.height=6, fig.width=12}
# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "KS")
